---
title: "Class6 R functions"
author: "Arpit Danewalia"
date: "10/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is H1
This is my work for class6 in **BIMM143**

```{r}
# this is to demo a code chunck
plot(1:10)
```


## Practice reading files (again....)
```{r}
read.csv("test1.txt", header=TRUE)
```
```{r}
read.table("test2.txt", sep= "$", header=TRUE)
```
needed to specify $ because in the text file the seperation is made using $ file 

```{r}
read.table("test3.txt")
```

```{r}
add <- function(x, y=1) {
  # Sum the input x and y 
  x + y
}
```

add function = (x value, y value) = add x+y
```{r}
add(1)
add(5,5)

add(c(1,2,3))
add(c(1,2,3),4)

#add(1, 2, 2)
#add(x=1, y="b")
```

A new function to re-scale data

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale(1:10)
```

```{r}
rescale(c(1,2,NA,3,10))
```

need to used the na.rm argument to make sure that all NA values are omitted

```{r}
x <- c(1,2,NA,3,10)
rng <- range(x, na.rm=TRUE)
rng
```

na.rm allows to rescale the values that are available and ignore the unavailable NA = unlike the original recale function

```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm=TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2(c(1,2,NA,3,10))
```

Too much...

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
  
    rng <-range(x, na.rm=na.rm)
    print("Hello")
 
    answer <- (x - rng[1]) / (rng[2] - rng[1])
 
    print("is it me you are looking for?")
 
    if(plot) {
        plot(answer, typ="b", lwd=4)
    }
    print("I can see it in ...")
    return(answer)
 
}
```

```{r}
rescale3(1:10, plot=TRUE)
```


```{r}
rescale4 <- function(x, na.rm=TRUE, plot=FALSE) {
  
    rng <-range(x, na.rm=na.rm)
    print("Hello")
 
    answer <- (x - rng[1]) / (rng[2] - rng[1])
    
    return(answer)
 
    print("is it me you are looking for?")
 
    if(plot) {
        plot(answer, typ="b", lwd=4)
    }
    print("I can see it in ...")
    return(answer)
 
}
```

```{r}
rescale4(1:10, plot=TRUE)
```

# Section2 of hands-on sheet

Install the **bio3d** package for sequence and structure analysis 
```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

In order to generalize the original code to fit any set of input protein structures the following code it used 
```{r}
#acessing information from the bio3d library database
library(bio3d)
#assigning the function performed on variable x, an unknown protien to readprotein. This is the base mechanism for defining new functions in R. The output is the ability to access information from the bio3d library database. 
readprotien <- function(x){
#assigning the function read.pdb(x), where x is the unknown protein to sx.The function read.pdb() reads a Protein Data Bank (PDB) coordinate file for the unknown protein. THe output is that sx is assigned to read.pbd(x)
  sx <- read.pdb(x)
#assigning the function trim.pdb(sx, chain="A", elety="CA") to sx.chainA to produce a new smaller PDB object, containing a subset chain A, from a given larger PDB object for the unknown protein. The output provides a PDB protein that is trimmed to a subset of atoms. 
  sx.chainA <- trim.pdb(sx, chain="A", elety="CA")
#assigning atom b from protein chain A for the unknown protein to sx.b. The output is provide sx.b assidned to chain A, atom b of the unknown protein. 
  sx.b <- sx.chainA$atom$b
#using the function plotb3 for the previously assigned unknown protein sx.b to draw a standard scatter plot with optional secondary structure in the marginal regions for the unknown protein. The additional factor defined here are the y axis labeled as Bfactor, the type of line used in the plot (here 1) and sse defines the sum of squared errors for sx.chainA. The output here is a scatterplot 
  plotb3(sx.b, sse=sx.chainA, typ="l", ylab="Bfactor")

}
```
```{r}
readprotien("4AKE")
```





